analysis-pilot

### 2023-08-16 code/analysis-pilot.Rmd
14:58

@@

```{r}
ggplot(data=accuracy, aes(x = Age.months, y=Laughs, color=Experimenter)) +
  geom_point()
```
```

>>>>

#scatterplot
ggplot(data=data_long, aes(x = time, y= percent, color=Experimenter)) +
  geom_point(size=1.5, alpha=.7) +
  geom_smooth(se=F) +
  theme_classic() +
  xlab("Age in months") +
  ylab("Number of Laughs") +
  theme(aspect.ratio = 3/5,
        axis.title=element_text(size=14,face="bold"),
        axis.text=element_text(size=12),
        legend.title=element_text(size=14,face="bold"),
        legend.text=element_text(size=12),
        legend.direction="horizontal",
        legend.position="bottom") +
  facet_wrap(~time)

@@

```
```
